---
title: "Online search interest in car brands: demographic determinants and state-specific effects"
output:
  html_document:
    df_print: paged
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Load Packages
```{r}
library(tidyverse)
library(gtrendsR)
library(readxl)
library(writexl)
library(spdep)
library(ggplot2)
library(car)
library(lmtest)
library(stargazer)
library(texreg)
library(rio)
```

<!-- ## Parameters -->
<!-- ```{r} -->
<!-- # enter keyword as it is reflected in the browser's address bar when you do it manually through trends.google.com -->
<!-- keywords1=c( -->
<!-- "%2Fg%2F120p4ddh", -->
<!-- "%2Fg%2F12pvlm8d0", -->
<!-- "%2Fg%2F12pvlm8br", -->
<!-- "%2Fm%2F04tnkz", -->
<!-- "%2Fm%2F04hpv1") -->

<!-- keywords2=c( -->
<!-- "%2Fm%2F0371q5", -->
<!-- "%2Fm%2F0266vgv", -->
<!-- "%2Fm%2F046fv7", -->
<!-- "%2Fm%2F06ryb5", -->
<!-- "%2Fm%2F01_pxf" -->
<!-- ) -->

<!-- # level of analysis -->
<!-- level="state" -->

<!-- # which survey to use -->
<!-- survey="acs1" -->
<!-- ``` -->

<!-- ## Google Trends data -->

<!-- Request Google Trends data for the topic of interest. -->
<!-- ```{r} -->
<!-- # empty lists -->
<!-- gtrends_states1<-list() -->
<!-- gtrends_states2<-list() -->

<!-- # collect data for many years to the list -->
<!-- for (i in c(2009:2019,2021)) { -->
<!-- gtrends_states1[[paste0("gtrends_states1_",i)]]<- -->
<!--        gtrends(keyword = keywords1, -->
<!--                geo = "US", -->
<!--                time = paste0(i,"-01-01 ",i,"-12-31"), -->
<!--                low_search_volume = TRUE)$interest_by_region%>% -->
<!--                mutate(YEAR=i) -->

<!-- gtrends_states2[[paste0("gtrends_states2_",i)]]<- -->
<!--        gtrends(keyword = keywords2, -->
<!--                geo = "US", -->
<!--                time = paste0(i,"-01-01 ",i,"-12-31"), -->
<!--                low_search_volume = TRUE)$interest_by_region%>% -->
<!--                mutate(YEAR=i) -->
<!-- } -->

<!-- # merge all  data frames comprising gtrends lists -->
<!-- gtrends_states1_df<-bind_rows(gtrends_states1) -->
<!-- gtrends_states2_df<-bind_rows(gtrends_states2) -->

<!-- gtrends_states<-bind_rows(gtrends_states1_df, -->
<!--                           gtrends_states2_df)%>% -->
<!-- dplyr::select(-geo,-gprop) -->
<!-- ``` -->

<!-- Convert keywords to "normal" words -->
<!-- ```{r} -->
<!-- keywords_replacement<-data.frame( -->
<!-- keyword=unique(gtrends_states$keyword), -->
<!-- keyword_2=c( -->
<!-- "Ford F-150", -->
<!-- "RAM 1500", -->
<!-- "Chevrolet Silverado 1500", -->
<!-- "Toyota RAV4", -->
<!-- "Honda CR-V", -->
<!-- "Toyota Camry", -->
<!-- "Nissan Rogue", -->
<!-- "Jeep Grand Cherokee", -->
<!-- "Toyota Highlander", -->
<!-- "Honda Civic" -->
<!-- )) -->

<!-- gtrends_states<-gtrends_states%>% -->
<!--   left_join(keywords_replacement)%>% -->
<!--   dplyr::select(-keyword)%>% -->
<!--   rename(keyword=keyword_2) -->

<!-- ``` -->

<!-- Create a database of state-level demographic characteristics using US census API. -->

<!-- ```{r} -->
<!-- # Load the tidycensus package into your R session -->
<!-- library(tidycensus) -->
<!-- # Define your Census API key and set it with census_api_key() -->
<!-- api_key <- "adb17a79927311f38e26b60b23cac8393a7af0a2" -->
<!-- census_api_key(api_key,install=TRUE,overwrite = TRUE) -->
<!-- ``` -->

<!-- Load the catalog of variables from 1-year ACS 2019. -->

<!-- ```{r} -->
<!-- readRenviron("~/.Renviron") -->
<!-- variables <- load_variables(2019, survey, cache = TRUE) -->

<!-- # create subfolder for outputs -->
<!-- dir.create(file.path("Outputs"), recursive = TRUE) -->

<!-- # save variables.csv for easy search of relevant ACS variables in Excel -->
<!-- write_xlsx(variables, "Outputs/variables.xlsx")  -->
<!-- ``` -->

<!-- Get ACS data on relevant variables -->

<!-- ```{r} -->
<!-- names<-c( -->
<!-- ### male counts -->
<!-- male_all="B01001_002", -->
<!-- male_0_4="B01001_003", -->
<!-- male_5_9="B01001_004", -->
<!-- male_10_14="B01001_005", -->
<!-- male_15_17="B01001_006", -->
<!-- male_18_19="B01001_007", -->
<!-- male_20="B01001_008", -->
<!-- male_21="B01001_009", -->
<!-- male_22_24="B01001_010", -->
<!-- male_25_29="B01001_011", -->
<!-- male_30_34="B01001_012", -->
<!-- male_35_39="B01001_013", -->
<!-- male_40_44="B01001_014", -->
<!-- male_45_49="B01001_015", -->
<!-- male_50_54="B01001_016", -->
<!-- male_55_59="B01001_017", -->
<!-- male_60_61="B01001_018", -->
<!-- male_62_64="B01001_019", -->
<!-- male_65_66="B01001_020", -->
<!-- male_67_69="B01001_021", -->
<!-- male_70_74="B01001_022", -->
<!-- male_75_79="B01001_023", -->
<!-- male_80_84="B01001_024", -->
<!-- male_85_over="B01001_025", -->

<!-- ### female counts -->
<!-- fem_all="B01001_026", -->
<!-- fem_0_4="B01001_027", -->
<!-- fem_5_9="B01001_028", -->
<!-- fem_10_14="B01001_029", -->
<!-- fem_15_17="B01001_030", -->
<!-- fem_18_19="B01001_031", -->
<!-- fem_20="B01001_032", -->
<!-- fem_21="B01001_033", -->
<!-- fem_22_24="B01001_034", -->
<!-- fem_25_29="B01001_035", -->
<!-- fem_30_34="B01001_036", -->
<!-- fem_35_39="B01001_037", -->
<!-- fem_40_44="B01001_038", -->
<!-- fem_45_49="B01001_039", -->
<!-- fem_50_54="B01001_040", -->
<!-- fem_55_59="B01001_041", -->
<!-- fem_60_61="B01001_042", -->
<!-- fem_62_64="B01001_043", -->
<!-- fem_65_66="B01001_044", -->
<!-- fem_67_69="B01001_045", -->
<!-- fem_70_74="B01001_046", -->
<!-- fem_75_79="B01001_047", -->
<!-- fem_80_84="B01001_048", -->
<!-- fem_85_over="B01001_049", -->

<!-- # total counts -->
<!-- total="B02001_001", -->

<!-- # race counts -->
<!-- white="B02001_002", -->
<!-- black="B02001_003", -->
<!-- asian="B02001_005", -->

<!-- # median income variables -->
<!-- med_fam_inc="B19113_001", -->
<!-- med_hh_inc="B19013_001") -->

<!-- # empty list -->
<!-- acs_states<-list() -->

<!-- # get ACS data on the features specified above -->
<!-- for (i in c(2009:2019,2021)) { -->
<!-- acs_states[[paste0("acs_states_",i)]]<- get_acs(level, -->
<!--                   variables=names, -->
<!--                   survey=survey, -->
<!--                   year=i, -->
<!--                   output = "wide")%>% -->
<!--                   dplyr::select(-ends_with("M"))%>% -->
<!--                   mutate(YEAR=i) -->
<!-- } -->

<!-- # merge all data frames from acs_states list -->
<!-- acs_states<-bind_rows(acs_states) -->
<!-- ``` -->

<!-- ## Join files to come up with the final data frame -->

<!-- ```{r} -->
<!-- data<-gtrends_states%>% -->
<!--   left_join(acs_states,by=c("location"="NAME","YEAR")) -->
<!-- ``` -->

<!-- ## Convert counts to % -->

<!-- ```{r} -->
<!-- ## Convert counts to % of total population -->
<!-- perc=dplyr::select(as.data.frame(data),male_allE:asianE)/ -->
<!--   rep(as.data.frame(data)[,which(colnames(as.data.frame(data))=="totalE")], -->
<!--       ncol(dplyr::select(as.data.frame(data),fem_allE:asianE)))*100 -->
<!-- colnames(perc)<-paste0("perc_",colnames(perc)) -->

<!-- library(dplyr) -->
<!-- data_final<-bind_cols(data[,c("keyword", -->
<!--                               "YEAR", -->
<!--                               "location", -->
<!--                               "hits", -->
<!--                               "med_fam_incE", -->
<!--                               "med_hh_incE")],perc)%>% -->
<!--   dplyr::select(-perc_totalE) -->
<!-- ``` -->

<!-- ## Rename variables, clean variable names -->
<!-- ```{r} -->
<!-- # remove E from the end of column names -->
<!-- colnames(data_final)<-str_replace(colnames(data_final), "E$", "") -->

<!-- # rename some columns -->
<!-- data_final<-data_final%>%dplyr::rename(interest=hits,state=location) -->

<!-- # lower case -->
<!-- colnames(data_final)<-tolower(colnames(data_final)) -->

<!-- # remove NAs -->
<!-- data_final<-na.omit(data_final) -->

<!-- # convert income variables to thousand dollars -->
<!-- data_final<-data_final%>%mutate(med_fam_inc=med_fam_inc/1000, -->
<!--                                 med_hh_inc=med_hh_inc/1000) -->
<!-- ``` -->

<!-- ## Save workspace and data file -->

<!-- ```{r} -->
<!-- # save workspace -->
<!-- save.image("Data_States.RData") -->

<!-- # save data to Excel -->
<!-- library(rio) -->
<!-- export(data_final,"data_final.xlsx",overwrite=T) -->
<!-- ``` -->

## Import data from Excel
```{r}
data_final<-import("gt_census.xlsx")
```

## Summary statistics

```{r}
library(stargazer)
# summary statistics for demographic variables
stargazer(as.data.frame(dplyr::select_if(data_final,is.numeric)),type="html",out="summary.htm")

# summary statistics for outcome variables
export(data_final%>%
  group_by(keyword)%>%
  summarise(mean_interest=mean(interest),
            sd_interest=sd(interest),
            min_interest=min(interest),
            p25_interest=quantile(interest,0.25),
            median_interest=quantile(interest,0.5),
            p75_interest=quantile(interest,0.75),
            max_interest=max(interest)),"summary_outcome.xlsx",overwrite=TRUE)
```

## Demean data by state and year
```{r}
# subtract state averages
data_final_demeaned<-data_final %>%
  group_by(keyword,state) %>%
  mutate(across(colnames(data_final)[-c(1:3)], 
                ~ .x - mean(.x), 
                .names = "{col}"))

# subtract year averages
data_final_demeaned<-data_final_demeaned %>%
  group_by(keyword,year) %>%
  mutate(across(colnames(data_final)[-c(1:3)], 
                ~ .x - mean(.x), 
                .names = "{col}"))
```

## Estimate rlasso models
```{r}
library(hdm)
coef=list()
i=0
for (k in unique(data_final_demeaned$keyword)){
  i=i+1
  model.lasso<-rlasso(interest~.,
                      data=subset(data_final_demeaned[,-c(2,3)],keyword==k)[,-1])
coef[[i]]<-coef(model.lasso)
}

# convert list of coefficients to data frame
names(coef)<-unique(data_final_demeaned$keyword)
coef2<- Map(cbind,coef, keyword =(names(coef)))
coefs<-bind_rows(coef2)
coefs$var=names(coef(model.lasso))

coefs<-as.data.frame(as.matrix(coefs))%>%
  dplyr::select(-contains("keyword"))

coefs<-pivot_longer(coefs,1:10,
               names_to="keyword",
               "values_to"="coef")

coefs$keyword<-gsub("\\.","",coefs$keyword)
coefs<-coefs%>%
  mutate(coef=as.numeric(coef))%>%
  filter((!coef==0)&(!var%in%c("(Intercept)","intercept")))
```

## Estimate 10 models selected by the rlasso procedure
```{r}
# list of keywords
keywords<-unique(data_final$keyword)

# convert year to factor
data_final$year=factor(data_final$year)


library(estimatr)
model1<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[1]],year,state),
keyword==keywords[1])[,-1])

model2<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[2]],year,state),
keyword==keywords[2])[,-1])

model3<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[3]],year,state),
keyword==keywords[3])[,-1])

model4<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[4]],year,state),
keyword==keywords[4])[,-1])

model5<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[5]],year,state),
keyword==keywords[5])[,-1])

model6<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[6]],year,state),
keyword==keywords[6])[,-1])

model7<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[7]],year,state),
keyword==keywords[7])[,-1])

model8<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[8]],year,state),
keyword==keywords[8])[,-1])

model9<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[9]],year,state),
keyword==keywords[9])[,-1])

model10<-lm(interest~.,
data=subset(dplyr::select(data_final,keyword,interest,
coefs$var[coefs$keyword==keywords[10]],year,state),
keyword==keywords[10])[,-1])


library(relaimpo)
imp1<-calc.relimp(model1,type="lmg",rela=TRUE)
imp2<-calc.relimp(model2,type="lmg",rela=TRUE)
imp3<-calc.relimp(model3,type="lmg",rela=TRUE)
imp4<-calc.relimp(model4,type="lmg",rela=TRUE)
imp5<-calc.relimp(model5,type="lmg",rela=TRUE)
imp6<-calc.relimp(model6,type="lmg",rela=TRUE)
imp7<-calc.relimp(model7,type="lmg",rela=TRUE)
imp8<-calc.relimp(model8,type="lmg",rela=TRUE)
imp9<-calc.relimp(model9,type="lmg",rela=TRUE)
imp10<-calc.relimp(model10,type="lmg",rela=TRUE)

imp_rlasso<-t(cbind(imp1@lmg[1:2],
      imp2@lmg[1:2],
      imp3@lmg[1:2],
      imp4@lmg[1:2],
      imp5@lmg[1:2],
      imp6@lmg[1:2],
      imp7@lmg[1:2],
      imp8@lmg[1:2],
      imp9@lmg[1:2],
      imp10@lmg[1:2]))


```

## Save tables with rlasso models to file
```{r include=FALSE}
stargazer(model1,
          model2,
          model3,
          model4,
          model5,
          se = starprep(model1,model2,model3,model4,model5),
          style="AER",
          column.labels = keywords_replacement$keyword_2[1:5],
          out="regressions_lasso1.htm")

stargazer(model6,
          model7,
          model8,
          model9,
          model10,
          se = starprep(model6,model7,model8,model9,model10),
          style="AER",
          column.labels = keywords_replacement$keyword_2[6:10],
          out="regressions_lasso2.htm")

```

## Regression table for 3 car models
```{r}
stargazer(model10,
          model4,
          model1,
          se = starprep(
          model10,
          model4,
          model1),
          style="AER",
          column.labels = keywords_replacement$keyword_2[c(10,4,1)],
          out="regressions_stepwise_final.htm",
          single.row = TRUE,
          digits=2)
```

## Stepwise models based on BIC minimization
```{r}
model1<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[1])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[1]))),
scope=list(lower=~year+state),
trace = 0)

model2<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[2])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[2]))),
scope=list(lower=~year+state),
trace = 0)

model3<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[3])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[3]))),
scope=list(lower=~year+state),
trace = 0)

model4<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[4])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[4]))),
scope=list(lower=~year+state),
trace = 0)

model5<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[5])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[5]))),
scope=list(lower=~year+state),
trace = 0)

model6<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[6])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[6]))),
scope=list(lower=~year+state),
trace = 0)

model7<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[7])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[7]))),
scope=list(lower=~year+state),
trace = 0)

model8<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[8])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[8]))),
scope=list(lower=~year+state),
trace = 0)

model9<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[9])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[9]))),
scope=list(lower=~year+state),
trace = 0)

model10<-step(lm(interest~.,
data=subset(data_final,
keyword==keywords[10])[,-1]),
k=log(nrow(subset(data_final,
keyword==keywords[10]))),
scope=list(lower=~year+state),
trace = 0)
```

## Relative importance in stepwise models
```{r}
library(relaimpo)
imp1<-calc.relimp(model1,type="lmg",rela=TRUE)
imp2<-calc.relimp(model2,type="lmg",rela=TRUE)
imp3<-calc.relimp(model3,type="lmg",rela=TRUE)
imp4<-calc.relimp(model4,type="lmg",rela=TRUE)
imp5<-calc.relimp(model5,type="lmg",rela=TRUE)
imp6<-calc.relimp(model6,type="lmg",rela=TRUE)
imp7<-calc.relimp(model7,type="lmg",rela=TRUE)
imp8<-calc.relimp(model8,type="lmg",rela=TRUE)
imp9<-calc.relimp(model9,type="lmg",rela=TRUE)
imp10<-calc.relimp(model10,type="lmg",rela=TRUE)

imp_stepwise<-t(cbind(imp1@lmg[1:2],
      imp2@lmg[1:2],
      imp3@lmg[1:2],
      imp4@lmg[1:2],
      imp5@lmg[1:2],
      imp6@lmg[1:2],
      imp7@lmg[1:2],
      imp8@lmg[1:2],
      imp9@lmg[1:2],
      imp10@lmg[1:2]))
```

## Save tables with stepwise regressions to file
```{r include=FALSE}
stargazer(model1,
          model2,
          model3,
          model4,
          model5,
          se = starprep(model1,
          model2,
          model3,
          model4,
          model5),
          style="AER",
          column.labels = keywords_replacement$keyword_2[1:5],
          out="regressions_stepwise1.htm",
          digits=2)


stargazer(model6,
          model7,
          model8,
          model9,
          model10,
          se = starprep(
          model6,
          model7,
          model8,
          model9,
          model10),
          style="AER",
          column.labels = keywords_replacement$keyword_2[6:10],
          out="regressions_stepwise2.htm",
          digits=2)
```

## Save importance table
```{r}
options(scipen=999)
relaimpo<-data.frame(Model=rep(keywords_replacement$keyword_2,2),
                     Method=c(rep("LASSO",10),rep("Stepwise",10)),
                     bind_rows(data.frame(imp_rlasso)*100,
                    data.frame(imp_stepwise)*100))%>%
  mutate(demography=100-state-year)


relaimpo_long<-relaimpo%>%
  pivot_longer(year:demography,
               names_to = "Factor",
               values_to="Contribution")

# order factor variable
relaimpo_long$Model<-factor(relaimpo_long$Model,
                            levels=relaimpo_long$Model[relaimpo_long$Factor=="demography"&relaimpo_long$Method=="LASSO"][order(relaimpo_long$Contribution[relaimpo_long$Factor=="demography"&relaimpo_long$Method=="LASSO"])])
  
```


```{r}
export(relaimpo,"relaimpo.xlsx",overwrite=TRUE)
```

## Visualize relative importance
```{r}
library(ggthemes)
ggplot(relaimpo_long%>%
         mutate_if(is.numeric,~round(.,digits=0)), 
       aes(fill=Factor,x=Contribution, y=Model))+ 
  geom_bar(position="fill",stat="identity")+
    facet_wrap(~Method)+
  labs(y="",x="\nProportion of explained variance")+
  theme_economist()+
  theme(panel.margin = unit(2, "lines"))
```



